IOIs Analysis: The Sound of Teaching Music 2

### 2020-01-06 script/RNotebook/ioi_3.Rmd
add stats
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

##### Description: This is a summary of all analyses for a tempo (IOIs).
  - data <- data_ioi_1.csv

@@

```{r extract, include = FALSE}
df_ioi <- read.csv("./trimmed/data_ioi_1.csv", header = T, sep = ",", dec = ".") # read a trimmed csv

@@

```{r ioi_art_ch, echo = FALSE}
# Define phrase boundaries
df_ioi_art$Boundary <- "No"
df_ioi_art$Boundary[df_ioi_dyn$Subcomponent == "LtoS" | df_ioi_dyn$Subcomponent == "StoL" | df_ioi_dyn$Subcomponent == "FtoP" | df_ioi_art$Subcomponent == "PtoF"] <- "Yes"

# For each individual
ioi_art_ch <- aggregate(normIOI~SubNr*Condition*Skill*Boundary, data = df_ioi_art,
                    FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_art_ch <- cbind(ioi_art_ch[,1:4], as.data.frame(ioi_art_ch[,5]))
# Change colnames
colnames(ioi_art_ch) <- c("SubNr", "Condition", "Skill", "Boundary", "N", "Mean", "SD")
print(ioi_art_ch)
```

@@

```{r ioi_dyn_ch, echo = FALSE}
df_ioi_dyn$Boundary <- "No"
df_ioi_dyn$Boundary[df_ioi_dyn$Subcomponent == "LtoS" | df_ioi_dyn$Subcomponent == "StoL" | df_ioi_dyn$Subcomponent == "FtoP" | df_ioi_dyn$Subcomponent == "PtoF"] <- "Yes"

# For each individual
ioi_dyn_ch <- aggregate(normIOI~SubNr*Condition*Skill*Boundary, data = df_ioi_dyn,
                    FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_dyn_ch <- cbind(ioi_dyn_ch[,1:4], as.data.frame(ioi_dyn_ch[,5]))
# Change colnames
colnames(ioi_dyn_ch) <- c("SubNr", "Condition", "Skill", "Boundary", "N", "Mean", "SD")
print(ioi_dyn_ch)
```

>>>>

##### Description: This is a summary of all analyses for a tempo (IOIs).
  - data <- data_ioi_3.csv

@@

```{r extract, include = FALSE}
df_ioi <- read.csv("./trimmed/data_ioi_3.csv", header = T, sep = ",", dec = ".") # read a trimmed csv

@@

```{r ioi_art_ch, echo = FALSE}
# For each individual
ioi_art_ch <- aggregate(normIOI~SubNr*Condition*Skill*Boundary, data = df_ioi_art,
                    FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_art_ch <- cbind(ioi_art_ch[,1:4], as.data.frame(ioi_art_ch[,5]))
# Change colnames
colnames(ioi_art_ch) <- c("SubNr", "Condition", "Skill", "Boundary", "N", "Mean", "SD")
print(ioi_art_ch)
```

@@

```{r ioi_dyn_ch, echo = FALSE}
# For each individual
ioi_dyn_ch <- aggregate(normIOI~SubNr*Condition*Skill*Boundary, data = df_ioi_dyn,
                    FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
ioi_dyn_ch <- cbind(ioi_dyn_ch[,1:4], as.data.frame(ioi_dyn_ch[,5]))
# Change colnames
colnames(ioi_dyn_ch) <- c("SubNr", "Condition", "Skill", "Boundary", "N", "Mean", "SD")
print(ioi_dyn_ch)
```
